---
title: "p8105_hw1_yz4433.Rmd"
author: "Yifei Zhao"
date: "2022-09-21"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

### Numerical Discussion
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
```
The dataset "penguins" shows the basic statistics of three penguins species. The "penguins" is a `r nrow(penguins)` $\times$ `r ncol(penguins)` dataset. The mean flipper length is 200.9mm except two NA values.

### Plotting
```{r}
img1 = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("img1.png", img1)
```

## Problem 2

### Create Dataframe
```{r}
x1 = rnorm(10)
x2 = c(x1 > 0)
x3 = c("abc", "123", "a dog", "ddd", NA, "nice9", "species", "island", "length", "width")
x4 = factor(c("top", "mid", "bot", "mid", "mid", "bot", "top", "bot", "top","mid"))
df2 = data.frame(x1, x2, x3, x4)
```

### Calculate the mean
```{r}
y1 = pull(df2,var=1)
mean(y1)
y2 = pull(df2,var=2)
mean(y2)
y3 = pull(df2,var=3)
mean(y3)
y4 = pull(df2,var=4)
mean(y4)
```
After calculation, we find the first two variables (a random sample of size 10 from a standard Normal distribution, and a logical vector indicating whether elements of the sample are greater than 0) work but the last two variables (a character vector of length 10, and a factor vector of length 10, with 3 different factor “levels”) do not work.

### Further discussions about converting variables
```{r echo=T, results='hide'}
z2 = as.numeric(y2)
z3 = as.numeric(y3)
z4 = as.numeric(y4)
```
After applying as.numeric function for these three variables, we find the character variable still does not work, but the factor variable works and no warning message appears. From my perspective, the numerical conversion works on the factor vector, but it does not work on converting character-type vector to numeric vector. Considering calculation for the mean, if the mean of variable can be calculated directly, the conversion will not change the mean. However, if the variable is a factor-type vector, the numerical conversion will help successfully calculate the mean level of factor vector, and for the character vector, it does not work successfully.